---
title: "Sample Immediate Feedback Report"
description: |
  This is super easy to create and edit!
author:
  - name: Dana Wanzer
    affiliation: Dana Wanzer Consulting
    url: http://danawanzer.com
date: October 29, 2018
output: 
  md_document:
  radix::radix_article:
    css: Blog_Template_Style.css
    toc: yes
always_allow_html: yes
---

```{r inclue = FALSE, echo = FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)

#Load packages
library(tidyverse)
library(knitr)
library(kableExtra)
library(scales)
library(apa)
library(janitor)

#Read in data from Survey Gizmo or Qualtrics Here
dat <- read.csv("Blog_Template_Data.csv")

#Remove the junk columns I don't need
dat <- dat %>%
  select(-c(2:21))
```

# Participant Learning

Please rating your knowledge or skills before and after the webinar.

```{r}
levels = c("Poor",
           "Fair", 
           "Good",
           "Very Good",
           "Excellent")

#Note the really horrible names coming from Survey Gizmo. I use the 'rename' function to fix these.
dat_PL <- dat %>%
  select(Before.the.webinar..I.would.rate.my.knowledge.or.skills.as..Rate.your.knowledge.or.skills.BEFORE.and.AFTER.the.webinar.Â., Now.after.the.webinar..I.would.rate.my.knowledge.or.skills.as..Rate.your.knowledge.or.skills.BEFORE.and.AFTER.the.webinar.Â.) %>%
  rename(Before = Before.the.webinar..I.would.rate.my.knowledge.or.skills.as..Rate.your.knowledge.or.skills.BEFORE.and.AFTER.the.webinar.Â., 
         After = Now.after.the.webinar..I.would.rate.my.knowledge.or.skills.as..Rate.your.knowledge.or.skills.BEFORE.and.AFTER.the.webinar.Â.) %>%
  mutate_all(factor, levels = levels)

dat_PL_nmean <- dat_PL %>% 
  mutate_all(funs(as.numeric(.))) %>%
  gather(Variable, value) %>% 
  group_by(Variable) %>% 
  filter(!is.na(value)) %>%
  summarise(n = n(),
            Mean = round(mean(as.numeric(value), na.rm = TRUE),2)) 

dat_PL_freq <- dat_PL %>%
  gather(Variable, value) %>%
  filter(!is.na(value)) %>%
  tabyl(Variable, value) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(digits = 0) %>%
  as.data.frame()

dat_PL_table <- list(dat_PL_nmean, dat_PL_freq) %>%
  reduce(full_join, by = "Variable") %>%
  arrange(Mean)

kable(dat_PL_table, 
      col.names = c("", "n", "Mean", levels),
      align = c('l', rep('r', times = 7))) %>% 
  kable_styling(full_width = TRUE, 
                position = "left")
```

```{r, echo = FALSE}
#Include a t-test comparison
dat_PL_ttest <- t.test(x = as.numeric(dat_PL$Before), y = as.numeric(dat_PL$After), paired = TRUE)
apattest <- apa(dat_PL_ttest)
```

The following shows the statistical difference between ratings of participants' knowledge or skills from before to after, as well as the Cohen's d effect size of the difference in ratings: `r apattest`.

# Open-Ended Items

This is all test data so it's meaningless, but participants' actual responses would go here instead. 

### What could be done to improve this webinar?

```{r}
Improve <- dat %>%
  select(What.could.be.done.to.improve.this.webinar.) %>%
  filter(What.could.be.done.to.improve.this.webinar. != "") %>%
  sample_n(10) %>%
  rownames_to_column() %>%
  select(What.could.be.done.to.improve.this.webinar.)

x <- kable(Improve,
      col.names = c("Response")) %>% 
  kable_styling(full_width = TRUE, 
                position = "left")
gsub("<thead>.*</thead>", "", x) #This removes the header from the table, which would just be 'x' or 'variable' otherwise
```

